\subsection{Datasets}

We evaluate TSFMs on six publicly available industrial PdM datasets spanning multiple domains and failure modes. Table~\ref{tab:datasets} summarizes the dataset characteristics.

\begin{table}[htbp]
\caption{Industrial PdM Dataset Summary}
\label{tab:datasets}
\centering
\begin{tabular}{lccccc}
\toprule
Dataset & Domain & Samples & Channels & Tasks & Failure Rate \\
\midrule
C-MAPSS & Turbofan & 100 & 21 & RUL/Forecast & 20\% \\
PHM Milling & CNC & 16k & 8 & Anomaly & 15\% \\
PU Bearings & Rotating & 32 & 4 & RUL/Anomaly & 32\% \\
Wind SCADA & Turbines & 6k & 52 & Forecast & 8\% \\
MIMII & Factory & 10k & 8 & Anomaly & 10\% \\
PRONOSTIA & Bearings & 17 & 3 & RUL & 100\% \\
\bottomrule
\end{tabular}
\end{table}

The C-MAPSS dataset~\cite{saxena2008cmapss} contains simulated run-to-failure trajectories of turbofan engines under varying operating conditions. Each trajectory includes 21 sensor channels measuring temperature, pressure, and flow rates. The PHM 2010 Milling dataset~\cite{phm2010milling} captures tool wear progression during CNC machining operations with 8 sensor channels including vibration and acoustic emission. The Paderborn University bearing dataset~\cite{lessmeier2016paderborn} provides high-frequency vibration data from bearings under controlled fault conditions. Wind SCADA data captures operational parameters from wind turbines, while MIMII~\cite{mimii2019} provides audio-based anomaly detection data from factory machinery.

\subsection{Models}

We evaluate six TSFMs representing different architectural approaches:
\begin{itemize}
    \item \textbf{MOMENT}~\cite{goswami2024moment}: 385M parameters, masked pretraining, multivariate support
    \item \textbf{Sundial}~\cite{ekambaram2024sundial}: Probabilistic forecasting with uncertainty quantification
    \item \textbf{Chronos}~\cite{ansari2024chronos}: Token-based approach inspired by LLMs
    \item \textbf{Time-MoE}~\cite{time_moe2024}: Mixture-of-experts for scalable temporal modeling
    \item \textbf{Lag-Llama,}~\cite{lag_llama2023}: Autoregressive language modeling for time series
    \item \textbf{TimeGPT}~\cite{garza2023timegpt}: API-based zero-shot forecasting service
\end{itemize}

We compare against three strong baselines: PatchTST~\cite{nie2022patchtst}, Autoformer~\cite{wu2021autoformer}, and a vanilla Transformer~\cite{vaswani2017attention}, all trained in supervised fashion on each dataset.

\subsection{SCADA Preprocessing Pipeline}

Our preprocessing pipeline addresses key challenges in industrial time series data:

\textbf{Chronological Splits:} We enforce strict chronological train/validation/test splits (70/15/15) with no shuffling to prevent temporal data leakage---a common pitfall in time series evaluation.

\textbf{Per-Sensor Normalization:} Industrial sensors operate at different scales and exhibit different noise characteristics. We apply Z-score normalization per sensor family, fitting statistics exclusively on training data to prevent information leakage.

\textbf{Kalman-Based Imputation:} Missing sensor readings are common in industrial settings due to sensor failures or communication drops. We employ forward-fill followed by linear interpolation, with column-mean fallback for persistent missing values.

\textbf{Sequence Construction:} We construct sliding window sequences with a lookback window of 512 time steps and a forecast horizon of 96 steps, matching the context length of most TSFMs.

\textbf{RUL Labeling:} For degradation datasets, we compute piecewise linear RUL labels capped at a maximum of 125 cycles, following the standard C-MAPSS protocol.

\subsection{Evaluation Protocol}

We evaluate models across three scenarios:

\textbf{Zero-Shot:} Direct inference without any task-specific adaptation, testing the claimed transfer capabilities of TSFMs.

\textbf{Few-Shot:} LoRA~\cite{hu2021lora} adaptation using only 1\% of training data (rank $r=16$, $\alpha=32$), simulating resource-constrained industrial settings where labeled data is scarce.

\textbf{Cross-Domain:} Training on one dataset and testing on another, evaluating the generalization capability across different industrial domains.

We report task-specific metrics: MAE, MSE, RMSE, and CRPS for forecasting; F1-score, AUC-ROC, and AUC-PR for anomaly detection; and MAE, RMSE, and Concordance Index (C-Index) for RUL prediction.
